---
title: "High Tech Marketing Text Analysis"
subtitle: "Brand: Motorola Razr 2025"
author: "Group 12?"
output:
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
#setup packages and stuff, include false so it doesn't show up.
# Set the CRAN mirror:
local({r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/"
  options(repos = r)}
)
# Install the packages used in this workbook:
packages <- c("RedditExtractoR", "httr", "jsonlite", "tidytext", "dplyr", "ggplot2", "wordcloud", "topicmodels", "LDAvis", "stringr")
for (i in packages) {
  if (!require(i, character.only = TRUE)) {
    install.packages(i, dependencies = TRUE)
    if (!require(i, character.only = TRUE)) {
      stop(paste("Package", i, "could not be loaded even after installation."))
    }
  }
}

#load the libraries
library(RedditExtractoR)
library(httr)
library(jsonlite)
library(tidytext)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(topicmodels)
library(LDAvis)
library(stringr)

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x
```

# Introduction
Explain shit here philippe 8=====D

# Sample Selection

## Data Sources
Explain which sources we used to grab the data and why these are good sources for the analysis

## Sampling representation & Bias
Explain if the sample is representative of all customers, and how platform choice may skew results e.g Reddit chuds are not normal people.

# Data Collection
```{r reddit-fetch, echo=TRUE}
fetch_reddit_thread <- function(thread_url, limit = 500, attempts = 5) {
  api_url <- paste0(thread_url, ".json?limit=", limit)
  response <- RETRY(
    "GET",
    api_url,
    user_agent("Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/125.0.0.0 Safari/537.36"),
    times = attempts,
    pause_base = 2,
    pause_cap = 20,
    terminate_on = c(400, 401, 403, 404)
  )

  if (http_error(response)) {
    stop("HTTP ", status_code(response), " when fetching ", api_url)
  }

  payload <- fromJSON(content(response, as = "text", encoding = "UTF-8"), simplifyVector = FALSE)
  post <- payload[[1]]$data$children[[1]]$data

  flatten_comments <- function(children) {
    if (!is.list(children)) {
      return(data.frame())
    }

    rows <- list()

    for (child in children) {
      if (!is.null(child$kind) && child$kind == "t1") {
        comment <- child$data
        rows[[length(rows) + 1]] <- data.frame(
          type = "comment",
          id = comment$id %||% NA_character_,
          parent_id = comment$parent_id %||% NA_character_,
          author = comment$author %||% NA_character_,
          body = comment$body %||% NA_character_,
          score = comment$score %||% NA_real_,
          created_utc = comment$created_utc %||% NA_real_,
          stringsAsFactors = FALSE
        )
        replies <- if (is.list(comment$replies) && !is.null(comment$replies$data$children)) {
          comment$replies$data$children
        } else {
          list()
        }
        if (length(replies) > 0) {
          rows <- c(rows, flatten_comments(replies))
        }
      }
    }

    if (length(rows) == 0) {
      return(data.frame())
    }

    do.call(rbind, rows)
  }

  comments <- flatten_comments(payload[[2]]$data$children %||% list())

  data.frame(
    type = c("post", comments$type),
    id = c(post$id %||% NA_character_, comments$id),
    parent_id = c(NA_character_, comments$parent_id),
    author = c(post$author %||% NA_character_, comments$author),
    body = c(post$selftext %||% post$title %||% NA_character_, comments$body),
    score = c(post$score %||% NA_real_, comments$score),
    created_utc = c(post$created_utc %||% NA_real_, comments$created_utc),
    stringsAsFactors = FALSE
  )
}

razr_posts <- tryCatch(
  find_thread_urls(keywords="motorola razr 2025", 
                   subreddit="Android", sort_by="top"),
  error = function(e) {
    message("Reddit search failed: ", conditionMessage(e))
    data.frame(url = character())
  }
)

razr_content <- if (nrow(razr_posts) > 0) {
  tryCatch(
    fetch_reddit_thread(razr_posts$url[1]),
    error = function(e) {
      message("Reddit content fetch failed: ", conditionMessage(e))
      data.frame()
    }
  )
} else {
  data.frame()
}

raw_df <- do.call(rbind, Filter(nrow, razr_content))

cat("Rows collected:", nrow(raw_df), "\n")
cat("Posts vs comments:\n")
print(table(raw_df$type))
```

```{r amazon-fetch, echo=TRUE}
# Placeholder for Amazon reviews fetching code
```

```{r youtube-fetch, echo=TRUE}
# Placeholder for YouTube comments fetching code
```

```{r twitter-fetch, echo=TRUE}
# Placeholder for Twitter mentions fetching code
```

# Pre-Processing
Side note maybe we dont have to do all of them based on the quality of the data we get, but we should at least explain how we would do them and why they are important.
## Filtering & Cleaning
Explain how we cleaned the data and why.

## Tokenization
Explain how we tokenized the data and why.

## Stop Words Removal
Explain how we removed stop words and why.

## Stemming & Lemmatization

## Frequency Filter

## Synonym consolidation

## Summary Statistics

# Topic Modeling (LDA)

## Build Document

## Optimal K

## Fit Model

## Stability

# Results

## Topic Word Distributions

## Sometother shit

# Reflection