---
title: "High Tech Marketing Text Analysis"
subtitle: "Brand: Motorola Razr 2025"
author: "Group 12?"
output:
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 7, fig.height = 4)

# Set the CRAN mirror:
local({r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/"
  options(repos = r)}
)

# Install the packages used in this workbook:
packages <- c("RedditExtractoR", "httr", "jsonlite", "tidytext", "dplyr",
              "ggplot2", "wordcloud", "topicmodels", "LDAvis", "stringr",
              "purrr", "quanteda", "sentimentr", "cld2", "seededlda",
              "textstem", "tidyr", "scales", "tibble")
for (i in packages) {
  if (!require(i, character.only = TRUE)) {
    install.packages(i, dependencies = TRUE)
    if (!require(i, character.only = TRUE)) {
      stop(paste("Package", i, "could not be loaded even after installation."))
    }
  }
}

# load the libraries
library(RedditExtractoR)
library(httr)
library(jsonlite)
library(tidytext)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(topicmodels)
library(LDAvis)
library(stringr)
library(purrr)
library(quanteda)
library(sentimentr)
library(seededlda)
library(cld2)
library(textstem)
library(tidyr)
library(scales)
library(tibble)

env_file <- ".env"
if (requireNamespace("knitr", quietly = TRUE)) {
  input_file <- knitr::current_input()
  if (!is.null(input_file)) {
    env_file <- file.path(dirname(input_file), ".env")
  }
}

if (file.exists(env_file)) {
  readRenviron(env_file)
} else if (file.exists(".env")) {
  readRenviron(".env")
}

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x
```

# Introduction

Technology fanatics on the internet have been known to be quite vocal of
their opinions, this usually takes shape when new smartphone's, gaming
consoles, or computers and their components are released. These vocal
opinions have especially been the case for foldable smartphones, wherein
the new Motorola RAZR's have been notable. Being a revival of the old
flip phone model, many individuals could have an emotional attachment to
the model and as such verbally share their thoughts on the new phone's.

# Sample Selection

This report shall be conducting a text analysis to gauge the consumer
sentiment of the new RAZR. In order to ensure that various diverse
perspectives are considered for the sentiment surrounding the RAZR
revival multiple sources of texts have been captured. This prevents the
risk of an echo-chamber like environment of impacting the data collected
and ultimately skewing the analysis results.

## Data Sources

The data used for the analysis have been gathered from two technology
dominant environments on the internet: Reddit and YouTube. From Reddit
threads which include the "Motorola Razr 2025" query was used under the
notion that it looks at threads which discuss the 2025 RAZR. Then for
YouTube comments were gathered from well known tech content creators
(such as Marques Brownlee) who reviewed the 2025 RAZR.

## Sampling representation & Bias

It must be acknowledged that there is a risk of an inherent bias being
introduced by choosing to look at both these specific platforms, and
user base. Of the large population of individuals who own smartphone's
many are not active on Reddit and even with regards to YouTube which
does have a larger install base, many are still not actively interacting
(posting or commenting). Individuals who are passionate or involved
enough to do either of the aforementioned actions could also be far more
critical than the average consumer. Though the case may also be made
that it is these exact tech fanatics who are active with the newest
technologies who would be the consumers for such a commodity as a
folding smartphone.

# Data Collection

Using the code chunk below Reddit is scraped for data which includes
certain key words which aid in the gathering of posts as well as
comments relating to the RAZR foldable. Key words such as "Android" and
"Motorola" are also crucial in ensuring that the data doesn't contain
either products from other companies which may also be called close to
RAZR (e.g. scooters) or even literal razors.

```{r reddit-fetch, echo=TRUE}
fetch_reddit_thread <- function(thread_url, limit = 500, attempts = 5) {
  api_url <- paste0(thread_url, ".json?limit=", limit)
  response <- RETRY(
    "GET",
    api_url,
    user_agent(paste0("Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) ",
                      "AppleWebKit/537.36 (KHTML, like Gecko) ",
                      "Chrome/125.0.0.0 Safari/537.36")),
    times        = attempts,
    pause_base   = 2,
    pause_cap    = 20,
    terminate_on = c(400, 401, 403, 404)
  )

  if (http_error(response)) {
    stop("HTTP ", status_code(response), " when fetching ", api_url)
  }

  payload <- fromJSON(
    content(response, as = "text", encoding = "UTF-8"),
    simplifyVector = FALSE
  )
  post <- payload[[1]]$data$children[[1]]$data

  flatten_comments <- function(children) {
    if (!is.list(children)) return(data.frame())
    rows <- list()
    for (child in children) {
      if (!is.null(child$kind) && child$kind == "t1") {
        comment   <- child$data
        body_text <- comment$body %||% NA_character_
        if (!is.null(body_text)) body_text <- gsub("[\r\n]+", " ", body_text)
        rows[[length(rows) + 1]] <- data.frame(
          type      = "comment",
          id        = comment$id        %||% NA_character_,
          parent_id = comment$parent_id %||% NA_character_,
          author    = comment$author    %||% NA_character_,
          body      = body_text,
          score     = comment$score     %||% NA_real_,
          subreddit = comment$subreddit %||% NA_character_,
          stringsAsFactors = FALSE
        )
        replies <- if (is.list(comment$replies) &&
                       !is.null(comment$replies$data$children))
          comment$replies$data$children else list()
        if (length(replies) > 0)
          rows <- c(rows, flatten_comments(replies))
      }
    }
    if (length(rows) == 0) return(data.frame())
    rows <- Filter(function(x) is.data.frame(x) && ncol(x) > 0, rows)
    if (length(rows) == 0) return(data.frame())
    tryCatch(
      dplyr::bind_rows(rows),
      error = function(e) {
        cols     <- c("type","id","parent_id","author","body","score","subreddit")
        repaired <- lapply(rows, function(r) {
          if (!is.data.frame(r)) return(NULL)
          for (m in setdiff(cols, names(r))) r[[m]] <- NA
          r[cols]
        })
        dplyr::bind_rows(Filter(Negate(is.null), repaired))
      }
    )
  }

  comments  <- flatten_comments(payload[[2]]$data$children %||% list())
  post_body <- post$selftext %||% post$title %||% NA_character_
  if (!is.null(post_body)) post_body <- gsub("[\r\n]+", " ", post_body)

  post_df <- data.frame(
    type      = "post",
    id        = post$id     %||% NA_character_,
    parent_id = NA_character_,
    author    = post$author %||% NA_character_,
    body      = post_body,
    score     = post$score  %||% NA_real_,
    subreddit = post$subreddit %||% NA_character_,
    stringsAsFactors = FALSE
  )

  if (!is.data.frame(comments)) comments <- data.frame()
  tryCatch(
    dplyr::bind_rows(post_df, comments),
    error = function(e) post_df
  )
}

suppressWarnings({
  reddit_cache <- "data/reddit_content.csv"
  cached <- file.exists(reddit_cache)

  if (cached) {
    reddit_all <- tryCatch(
      read.csv(reddit_cache, stringsAsFactors = FALSE),
      error = function(e) { message("Cache read failed: ", conditionMessage(e)); data.frame() }
    )
  } else {
    search_config <- list(
      list(sub = "Android",       kw = "motorola razr"),
      list(sub = "Android",       kw = "razr 2025"),
      list(sub = "Android",       kw = "razr flip"),
      list(sub = "Motorola",      kw = "razr"),
      list(sub = "Motorola",      kw = "razr ultra"),
      list(sub = "Motorola",      kw = "razr plus"),
      list(sub = "phones",        kw = "razr"),
      list(sub = "phones",        kw = "motorola"),
      list(sub = "smartphones",   kw = "motorola razr"),
      list(sub = "razr",          kw = "razr"),
      list(sub = "razr",          kw = "motorola"),
      list(sub = "technology",    kw = "motorola razr"),
      list(sub = "technology",    kw = "razr 2025")
    )

    reddit_posts <- dplyr::bind_rows(Filter(
      function(x) is.data.frame(x) && nrow(x) > 0,
      lapply(search_config, function(cfg) {
        result <- tryCatch({
          Sys.sleep(2)
          find_thread_urls(keywords = cfg$kw, subreddit = cfg$sub, sort_by = "top")
        }, error = function(e) {
          message("Failed r/", cfg$sub, " / '", cfg$kw, "': ", conditionMessage(e))
          data.frame(url = character())
        })
        if (!is.data.frame(result)) return(data.frame(url = character()))
        result
      })
    )) |> dplyr::distinct(url, .keep_all = TRUE)

    reddit_max_threads <- 250

    if (nrow(reddit_posts) > 0) {
      to_fetch <- head(reddit_posts$url, reddit_max_threads)
      raw_list <- lapply(seq_along(to_fetch), function(i) {
        Sys.sleep(1)
        tryCatch(
          fetch_reddit_thread(to_fetch[i]),
          error = function(e) { message("Failed: ", conditionMessage(e)); data.frame() }
        )
      })
      reddit_all <- dplyr::bind_rows(
        Filter(function(x) is.data.frame(x) && nrow(x) > 0, raw_list)
      )
    } else {
      reddit_all <- data.frame()
    }

    if (!dir.exists("data")) dir.create("data")
    write.csv(reddit_all, reddit_cache, row.names = FALSE)
  }
})

cat("Reddit total rows:", nrow(reddit_all), "\n")
cat("Posts vs comments:\n");  print(table(reddit_all$type))
cat("By subreddit:\n");       print(table(reddit_all$subreddit))
```

The same is done for YouTube in the code chunk below. Though it is
somewhat simpler, given that unlike Reddit where a plethora of posts and
comments must be scraped individually, on YouTube only comments for
specific known video's are observed. The selected video's themselves
correspond with content creators who have a reputation for being
trustworthy with unbiased reviews.

```{r youtube-fetch, echo=TRUE}
fetch_youtube_comments <- function(video_id, max_comments = 400, api_key = Sys.getenv("YOUTUBE_KEY")) {
  if (identical(api_key, "")) {
    stop("YOUTUBE_KEY is not set. Load it from .env or your environment before knitting.")
  }

  all_comments <- list()
  page_token   <- NULL

  repeat {
    query <- list(
      part       = "snippet",
      videoId    = video_id,
      maxResults = 100,
      textFormat = "plainText",
      key        = api_key
    )
    if (!is.null(page_token)) query$pageToken <- page_token

    resp <- httr::GET("https://www.googleapis.com/youtube/v3/commentThreads",
                      query = query)

    if (httr::http_error(resp)) {
      error_body <- tryCatch(httr::content(resp, as = "text", encoding = "UTF-8"),
                             error = function(e) "")
      message("YouTube API error: ", httr::status_code(resp),
              if (nzchar(error_body)) paste0(" - ", error_body) else "")
      break
    }

    parsed <- jsonlite::fromJSON(
      httr::content(resp, as = "text", encoding = "UTF-8"),
      flatten = TRUE
    )

    items <- parsed$items
    if (is.null(items) || nrow(items) == 0) break

    batch <- data.frame(
      comment_id = items$id,
      author     = items$snippet.topLevelComment.snippet.authorDisplayName,
      body       = items$snippet.topLevelComment.snippet.textDisplay,
      like_count = items$snippet.topLevelComment.snippet.likeCount,  # kept for segmentation
      stringsAsFactors = FALSE
    )

    all_comments[[length(all_comments) + 1]] <- batch
    collected <- sum(sapply(all_comments, nrow))

    page_token <- parsed$nextPageToken
    if (is.null(page_token) || collected >= max_comments) break
    Sys.sleep(0.5)
  }

  if (length(all_comments) == 0) return(data.frame())
  dplyr::bind_rows(all_comments) |> dplyr::mutate(source = "youtube")
}

razr_videos <- list(
  mkbhd      = "8om1eJrO2lU",   # MKBHD Razr 2025 review
  dave2d     = "JTT67FSc8j8",   # ShortCircuit review
  mrmobile   = "YGTkjchlVJk",   # MrMobile review
  phonearena = "b3Ijuf7DHcQ"    # PhoneArena review
)

if (file.exists("data/youtube_comments.csv")) {
  youtube_all <- read.csv("data/youtube_comments.csv", stringsAsFactors = FALSE)
  cat("Loaded YouTube comments from CSV:", nrow(youtube_all), "\n")
} else {
  youtube_all <- purrr::map2_dfr(
    razr_videos,
    names(razr_videos),
    ~ fetch_youtube_comments(.x, max_comments = 400) |>
        dplyr::mutate(channel = .y)
  )
  if (!dir.exists("data")) dir.create("data")
  write.csv(youtube_all, "data/youtube_comments.csv", row.names = FALSE)
}

cat("YouTube comments collected:", nrow(youtube_all), "\n")
print(table(youtube_all$channel))
```

# Exploration

With the initial scraping completed, attention may now be given to the
raw data which has been collected. While it may not yet provide any
useful conclusions, it can already provide some insight on the split
between the collected data. While there is a discrepancy between the raw
corpus volumes, it is not a magnitude which would be of concern in our
view.

```{r exploration, echo=TRUE}
exploration_summary <- tibble::tibble(
  Source    = c("Reddit (comments only)", "YouTube"),
  Documents = c(sum(reddit_all$type == "comment", na.rm = TRUE),
                nrow(youtube_all)),
  Avg_chars = c(round(mean(nchar(reddit_all$body[reddit_all$type == "comment"]), na.rm = TRUE), 1),
                round(mean(nchar(youtube_all$body), na.rm = TRUE), 1))
)
knitr::kable(exploration_summary, caption = "Raw corpus volume by source")
```

# Pre-Processing

As was mentioned previously, the data currently exists in two separate
data frames; the Reddit and YouTube data. In the code chunk below these
two are merged to create one large database to be used for further text
analyses. In order to still maintain some tractability between the data
a new column shall be added to indicate which source the data was
collected from and then binding them together. Furthermore an overview
may be provided for the languages comments are left in, which shall be
filtered and removed accordingly later on.

```{r merge-data, echo=FALSE}
# Reddit: keep only real comments, drop deleted/removed and very short text.
reddit_clean <- reddit_all |>
  filter(type == "comment", !is.na(body),
         body != "[deleted]", body != "[removed]",
         nchar(trimws(body)) > 20) |>
  select(author, body, score, subreddit) |>
  rename(source = subreddit)

# YouTube: use like_count as the engagement score, channel as the source.
youtube_clean <- youtube_all |>
  mutate(score  = if ("like_count" %in% names(youtube_all)) like_count else NA_real_,
         source = channel) |>
  select(author, body, score, source)

combined_data <- dplyr::bind_rows(reddit_clean, youtube_clean) |>
  mutate(id = row_number())

# Platform label (Reddit vs YouTube) for clean between-group tests later.
yt_channels <- c("mkbhd", "dave2d", "mrmobile", "phonearena")
combined_data <- combined_data |>
  mutate(platform = ifelse(source %in% yt_channels, "YouTube", "Reddit"))

# Language detection
combined_data$language <- cld2::detect_language(combined_data$body)
print(table(combined_data$language))

```

Side note maybe we dont have to do all of them based on the quality of
the data we get, but we should at least explain how we would do them and
why they are important.

I suppose, you got that tho twin \<3

## Filtering & Cleaning

The data may now be filtered by various means. From maintaining only
data in English, removing empty data points, to removing non-ASCII
characters, the data balanced is slightly shifted but not to concerning
bounds.

```{r data-cleaning, echo=TRUE}
# Keep English only
combined_data <- combined_data |> filter(language == "en")

# Strip non-ASCII characters
combined_data$body <- gsub("[^\x01-\x7F]", "", combined_data$body)

# Remove now-empty bodies
combined_data <- combined_data |> filter(body != "")

# Old vs. New era 
# Flag documents that reference the original
old_terms <- c("original", "old razr", "2004", "2005", "v3",
               "flip phone days", "back in the day", "nostalgia",
               "first razr", "classic", "used to have", "the old one")
combined_data <- combined_data |>
  mutate(era = ifelse(
    grepl(paste(old_terms, collapse = "|"), body, ignore.case = TRUE),
    "references_old", "new_only"))

cat("Era distribution (old-brand references vs new-only):\n")
print(table(combined_data$era))
cat("\nDocuments by platform:\n")
print(table(combined_data$platform))
```

# Modeling

With the collected data now filtered and cleaned up, work may be done on
the actual modelling of the text analysis.

## Corpus Creation

```{r corpus-creation, echo=TRUE}
corpus <- quanteda::corpus(combined_data, docid_field = "id", text_field = "body")

quanteda::docvars(corpus, field = "ave_sentiment") <-
  sentimentr::sentiment_by(sentimentr::get_sentences(corpus))$ave_sentiment

# Distribution of sentiment across the corpus
ggplot(data.frame(s = quanteda::docvars(corpus)$ave_sentiment),
       aes(x = s)) +
  geom_histogram(bins = 30, fill = "#2C7BB6") +
  labs(title = "Distribution of document sentiment",
       x = "Average sentiment", y = "Count") +
  theme_minimal()
```

## Tokenization

Explain how we tokenized the data and why.

```{r tokenization}
tokens <- quanteda::tokens(corpus,
                           what = "word",
                           remove_punct = TRUE,
                           remove_symbols = TRUE,
                           remove_numbers = TRUE,
                           remove_url = TRUE,
                           remove_separators = TRUE,
                           split_hyphens = FALSE,
                           split_tags = FALSE,
                           include_docvars = TRUE,
                           padding = FALSE,
                           verbose = FALSE)

tokens <- quanteda::tokens_tolower(tokens)
```

## Synonym consolidation

Now the tokens are also consolidated based on if they are synonyms of
other collected words. This aids in getting a clearer consensus of the
items which really matter for the consumers, since a camera is just
important as a cam.

```{r synonym-consolidation, echo=TRUE}
tokens <- quanteda::tokens_replace(tokens,
  pattern = c(
    "foldable", "folding",
    "flipping",
    "cam", "cams",
    "charging", "charger",
    "displays",
    "hinges", "hinging",
    "pricing", "priced", "pricey", "expensive", "costly",
    "galaxy",
    "ios", "apple"
  ),
  replacement = c(
    "fold", "fold",
    "flip",
    "camera", "camera",
    "charge", "charge",
    "display",
    "hinge", "hinge",
    "price", "price", "price", "price", "price",
    "samsung",
    "apple", "apple"
  ),
  valuetype = "fixed")
```

## Stop Words Removal

The data still includes a plethora of words which work to provide
structure to sentences, but in the context of data modelling serve
little to no purpose. These stop words are removed accordingly, as well
as certain key words which were required to obtain the data specifically
relating to the Motorola RAZR but serve little purpose now as well.

```{r stop-words, echo=TRUE}
custom_stops <- c(
  "razr", "motorola", "phone", "just", "get", "like", "thing", "really",
  "know", "time", "people", "would", "also", "much", "use", "see",
  "one", "will", "can", "even", "still", "want", "review",
  "moto", "device", "smartphone", "im", "dont", "ive", "thats", "got",
  "amp", "u", "ur", "ok", "yeah", "lol", "gonna", "good", "make",
  "think", "need", "look", "come", "say"
)
tokens <- quanteda::tokens_remove(
  tokens, pattern = c(quanteda::stopwords("en"), custom_stops))
```

## Stemming & Lemmatization

```{r stemming, echo=TRUE}
feats <- quanteda::types(tokens)
tokens <- quanteda::tokens_replace(
  tokens,
  pattern     = feats,
  replacement = textstem::lemmatize_words(feats),
  valuetype   = "fixed")
```

## DFM Creation & Frequency Filtering

```{r frequency-filter, echo=TRUE}
dfm <- quanteda::dfm(tokens)

# Keep only tokens of 3+ characters
dfm <- quanteda::dfm_select(dfm, pattern = "^.{3,}$",
                            valuetype = "regex", selection = "keep")

cat("Features before frequency trim:", nfeat(dfm), "\n")
# Drop very rare terms (appear fewer than 10) 
dfm <- dfm_trim(dfm, min_termfreq = 10)
cat("Features after frequency trim:", nfeat(dfm), "\n")

cat("\nMost frequent features:\n")
print(topfeatures(dfm, 15))

# Drop any documents left empty after all filtering
empty_docs <- which(rowSums(dfm) == 0)
if (length(empty_docs) > 0) dfm <- dfm[-empty_docs, ]
cat("\nFinal DFM:", ndoc(dfm), "documents x", nfeat(dfm), "features\n")
```

## Selecting K

```{r selecting-k, echo=TRUE}
dtm <- quanteda::convert(dfm, to = "topicmodels")

set.seed(42)
n_docs    <- nrow(dtm)
train_idx <- sample(n_docs, floor(n_docs * 0.8))
dtm_train <- dtm[train_idx, ]
dtm_test  <- dtm[-train_idx, ]

k_values <- 2:15
perplexity_scores <- sapply(k_values, function(k) {
  m <- topicmodels::LDA(dtm_train, k = k, method = "Gibbs",
                        control = list(seed = 42, iter = 1000, burnin = 200))
  topicmodels::perplexity(m, newdata = dtm_test)
})

perplexity_df <- data.frame(k = k_values, perplexity = perplexity_scores) |>
  mutate(improvement = dplyr::lag(perplexity) - perplexity)

ggplot(perplexity_df, aes(x = k, y = perplexity)) +
  geom_line(colour = "#2C7BB6") +
  geom_point(colour = "#2C7BB6", size = 2) +
  geom_vline(xintercept = 7, linetype = "dashed", colour = "red") +
  labs(title = "Held-out Perplexity by Number of Topics (k)",
       subtitle = "Dashed line = chosen k (elbow)",
       x = "k", y = "Perplexity") +
  theme_minimal()

knitr::kable(perplexity_df, digits = 2,
             caption = "Held-out perplexity and per-step improvement by k")
```

## LDA

```{r topic-modeling, echo=TRUE}
K <- 7

set.seed(42)
lda_model <- seededlda::textmodel_lda(dfm, k = K)

topic_assignments <- data.frame(
  doc_id    = docnames(dfm),
  topic     = topics(lda_model),
  sentiment = docvars(dfm)$ave_sentiment,
  stringsAsFactors = FALSE
)
```

## Stability Analysis

```{r stability-analysis, echo=TRUE}
seeds <- c(42L, 123L, 999L)

stability_results <- lapply(seeds, function(s) {
  set.seed(s)
  m     <- seededlda::textmodel_lda(dfm, k = K)
  trms  <- seededlda::terms(m, 5)
  apply(trms, 2, paste, collapse = ", ")
})

stability_df <- data.frame(
  topic    = paste0("Topic ", 1:K),
  seed_42  = stability_results[[1]],
  seed_123 = stability_results[[2]],
  seed_999 = stability_results[[3]],
  row.names = NULL
)

knitr::kable(stability_df,
             col.names = c("Topic", "Seed 42", "Seed 123", "Seed 999"),
             caption   = "Top 5 words per topic across 3 seeds (stability check)")
```

# Results

Having completed the modelling analyses, the results may now be
highlighted. From the individual words or topics, towards their relation
to overall consumer sentiment, the results shall show valuable insights
on just how the posters feel towards the revived RAZR.

## Topic Labels

Firstly seven various topics may be created and assigned with terms
which relate closely to said topics. The code chunk below highlights the
topics themselves as well as the top 10 most frequent terms which appear
per topic.

```{r topic-labels, echo=TRUE}
# Top 10 terms per topic
topic_terms <- seededlda::terms(lda_model, 10)
knitr::kable(topic_terms, caption = "Top 10 terms per topic")

# Labels 
topic_labels <- c(
  "topic1" = "Durability & Build Quality issues",
  "topic2" = "Form Factor & Design",
  "topic3" = "Competitor Comparison",
  "topic4" = "Hardware & Specs",
  "topic5" = "Price & Purchase",
  "topic6" = "Apps & Functionality",
  "topic7" = "Software & Support"
)
```

## Topic Word Distributions

Continuing with the seven topics the distribution of the top ten terms
may now be shown. Rather than just showing them in a ranked order one
may now also see just how important the various terms are for the
posters. As one might expect the code chunk below shows that a great
point of importance for the consumers for the foldable phone is the
screen, fold, and flip.

```{r topic-word-dist, echo=TRUE, fig.height=7}
# Extract per-topic word probabilities
phi <- lda_model$phi
beta_df <- as.data.frame(t(phi)) |>
  tibble::rownames_to_column("term") |>
  tidyr::pivot_longer(-term, names_to = "topic", values_to = "beta") |>
  group_by(topic) |>
  slice_max(beta, n = 8, with_ties = FALSE) |>
  ungroup() |>
  mutate(label = topic_labels[topic])

ggplot(beta_df,
       aes(x = tidytext::reorder_within(term, beta, topic),
           y = beta, fill = label)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~label, scales = "free_y") +
  coord_flip() +
  tidytext::scale_x_reordered() +
  labs(title = "Top terms per topic (word probability, beta)",
       x = NULL, y = "beta") +
  theme_minimal()
```

## Topic Prominence

Sticking with the seven topics, they are now cross-referenced to each
other. This will aid in showing just how important each of these topics
themselves are to the consumers, at least in how prominently they're
mentioned. The code chunk below shows that the most prominent topic is
for "Apps & Functionality", with the least prominent one being the
"Software & Support". This is interesting in showing that the actual
functioning of the device is a greater point of discussion, which would
make sense given the RAZR would simply run a variant of well established
Android OS.

```{r topic-prominence, echo=TRUE}
topic_counts <- as.data.frame(table(topics(lda_model))) |>
  rename(topic = Var1, n = Freq) |>
  mutate(prop  = n / sum(n),
         label = topic_labels[as.character(topic)])

ggplot(topic_counts, aes(x = reorder(label, prop), y = prop)) +
  geom_col(fill = "#2C7BB6") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Topic Prominence",
       x = NULL, y = "Proportion of documents") +
  theme_minimal()

knitr::kable(topic_counts |> select(label, n, prop),
             digits = 3, col.names = c("Topic", "N", "Proportion"),
             caption = "Relative prominence of each topic")
```

## Sentiment by Topic

A

```{r sentiment-by-topic, echo=TRUE}
topic_sentiment <- topic_assignments |>
  group_by(topic) |>
  summarise(mean_sentiment = mean(sentiment, na.rm = TRUE),
            n = n(), .groups = "drop") |>
  mutate(label = topic_labels[topic])

ggplot(topic_sentiment, aes(x = reorder(label, mean_sentiment), y = mean_sentiment)) +
  geom_col(fill = "#2C7BB6") +
  coord_flip() +
  labs(title = "Average Sentiment by Topic",
       x = NULL, y = "Average sentiment") +
  theme_minimal()

ggplot(topic_assignments |> mutate(label = topic_labels[topic]),
       aes(x = label, y = sentiment)) +
  geom_boxplot(fill = "#2C7BB6") +
  coord_flip() +
  labs(title = "Sentiment Distribution by Topic",
       x = NULL, y = "Sentiment") +
  theme_minimal()
```

## Statistical Tests

Through much of the data collecting and filtering brief mentions were
given on the data split between Reddit and YouTube. These were primarily
numerical, but how does their data differ inherently? That is what will
be explored below statistically.

### Do Reddit and YouTube discuss different topics?

With Reddit and YouTube having inherently different user bases, one
would assume that their topics of prominence would also differ. The code
chunk below serves to illustrate that Reddit is far more interested in
software and its comparison to competitors, while YouTube users focus
much more on physical aspects such as build quality and hardware
specifications. This could be as a result that Reddit is often used for
software support, whereas YouTube is used for real world tutorials.

```{r test-chisq, echo=TRUE}
topic_source <- topic_assignments |>
  mutate(doc_id = as.integer(doc_id)) |>
  left_join(combined_data |> select(id, platform, era),
            by = c("doc_id" = "id")) |>
  mutate(label = topic_labels[topic])

contingency <- table(topic_source$label, topic_source$platform)
knitr::kable(contingency, caption = "Topic distribution: Reddit vs YouTube")

chi_result <- chisq.test(contingency)
print(chi_result)
```

### Does sentiment differ across topics?

```{r test-kruskal, echo=TRUE}
kw_result <- kruskal.test(sentiment ~ factor(topic), data = topic_assignments)
print(kw_result)

pw <- pairwise.wilcox.test(topic_assignments$sentiment,
                           topic_assignments$topic,
                           p.adjust.method = "BH")
print(pw)
```

### Old vs New Era: does sentiment differ?

```{r test-era, echo=TRUE}
era_sentiment <- topic_source |>
  filter(!is.na(era))

cat("Sample sizes by era:\n")
print(table(era_sentiment$era))

# Wilcoxon rank-sum (non-parametric, two groups)
if (length(unique(era_sentiment$era)) == 2 &&
    all(table(era_sentiment$era) > 5)) {
  era_test <- wilcox.test(sentiment ~ era, data = era_sentiment)
  print(era_test)
} else {
  cat("Not enough old-brand references for a reliable test.\n")
}

# Mean sentiment by era
era_sentiment |>
  group_by(era) |>
  summarise(mean_sentiment = mean(sentiment, na.rm = TRUE),
            n = n(), .groups = "drop") |>
  knitr::kable(digits = 3, caption = "Sentiment: old-brand references vs new-only")
```

## Customer Value Triad

To conclude, attention is given to the 'customer value triad' (quality,
price, service), and what their share is of the corpus. What the chunk
below shows is two major conclusions: the quality aspect easily
dominates the corpus, and the service aspect is completely neglected.
This may also speak to the appeal of either the RAZR or Motorola as a
whole, and what is either of importance or relevance to their consumers.

```{r value-triad, echo=TRUE}
triad_map <- data.frame(
  topic = paste0("topic", 1:7),
  dimension = c("Quality",   # Durability & Build Quality
                "Quality",   # Form Factor & Design
                "Quality",   # Competitor Comparison
                "Quality",   # Hardware & Specs
                "Price",     # Price & Purchase
                "Quality",   # Apps & Functionality
                "Quality"))  # Software & Support

#nobody is talking about the servicwe and support aspect lmao
triad_summary <- topic_counts |>
  mutate(topic = as.character(topic)) |>   # already "topic1", just coerce factor->char
  left_join(triad_map, by = "topic") |>
  group_by(dimension) |>
  summarise(total_prop = sum(prop), .groups = "drop")

ggplot(triad_summary, aes(x = reorder(dimension, total_prop), y = total_prop)) +
  geom_col(fill = "#2C7BB6") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Customer Value Triad coverage",
       x = NULL, y = "Share of corpus") +
  theme_minimal()

knitr::kable(triad_summary, digits = 3,
             col.names = c("Value dimension", "Share of corpus"),
             caption = "Customer value triad reconstructed from topics")
```

# Reflection
