---
title: "High Tech Marketing Text Analysis"
subtitle: "Brand: Motorola Razr 2025"
author: "Group 12?"
output:
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
#setup packages and stuff, include false so it doesn't show up.
# Set the CRAN mirror:
local({r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/"
  options(repos = r)}
)
# Install the packages used in this workbook:
packages <- c("RedditExtractoR", "httr", "jsonlite", "tidytext", "dplyr", "ggplot2", "wordcloud", "topicmodels", "LDAvis", "stringr")
for (i in packages) {
  if (!require(i, character.only = TRUE)) {
    install.packages(i, dependencies = TRUE)
    if (!require(i, character.only = TRUE)) {
      stop(paste("Package", i, "could not be loaded even after installation."))
    }
  }
}

#load the libraries
library(RedditExtractoR)
library(httr)
library(jsonlite)
library(tidytext)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(topicmodels)
library(LDAvis)
library(stringr)

env_file <- ".env"
if (requireNamespace("knitr", quietly = TRUE)) {
  input_file <- knitr::current_input()
  if (!is.null(input_file)) {
    env_file <- file.path(dirname(input_file), ".env")
  }
}

if (file.exists(env_file)) {
  readRenviron(env_file)
} else if (file.exists(".env")) {
  readRenviron(".env")
}

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x
```

# Introduction
Explain shit here philippe 8=====D

# Sample Selection

## Data Sources
Explain which sources we used to grab the data and why these are good sources for the analysis

## Sampling representation & Bias
Explain if the sample is representative of all customers, and how platform choice may skew results e.g Reddit chuds are not normal people.

# Data Collection
```{r reddit-fetch, echo=TRUE}
fetch_reddit_thread <- function(thread_url, limit = 500, attempts = 5) {
  api_url <- paste0(thread_url, ".json?limit=", limit)
  response <- RETRY(
    "GET",
    api_url,
    user_agent("Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/125.0.0.0 Safari/537.36"),
    times = attempts,
    pause_base = 2,
    pause_cap = 20,
    terminate_on = c(400, 401, 403, 404)
  )

  if (http_error(response)) {
    stop("HTTP ", status_code(response), " when fetching ", api_url)
  }

  payload <- fromJSON(content(response, as = "text", encoding = "UTF-8"), simplifyVector = FALSE)
  post <- payload[[1]]$data$children[[1]]$data

  flatten_comments <- function(children) {
    if (!is.list(children)) {
      return(data.frame())
    }

    rows <- list()

    for (child in children) {
      if (!is.null(child$kind) && child$kind == "t1") {
        comment <- child$data
        rows[[length(rows) + 1]] <- data.frame(
          type = "comment",
          id = comment$id %||% NA_character_,
          parent_id = comment$parent_id %||% NA_character_,
          author = comment$author %||% NA_character_,
          body = comment$body %||% NA_character_,
          score = comment$score %||% NA_real_,
          created_utc = comment$created_utc %||% NA_real_,
          stringsAsFactors = FALSE
        )
        replies <- if (is.list(comment$replies) && !is.null(comment$replies$data$children)) {
          comment$replies$data$children
        } else {
          list()
        }
        if (length(replies) > 0) {
          rows <- c(rows, flatten_comments(replies))
        }
      }
    }

    if (length(rows) == 0) {
      return(data.frame())
    }

    do.call(rbind, rows)
  }

  comments <- flatten_comments(payload[[2]]$data$children %||% list())

  data.frame(
    type = c("post", comments$type),
    id = c(post$id %||% NA_character_, comments$id),
    parent_id = c(NA_character_, comments$parent_id),
    author = c(post$author %||% NA_character_, comments$author),
    body = c(post$selftext %||% post$title %||% NA_character_, comments$body),
    score = c(post$score %||% NA_real_, comments$score),
    created_utc = c(post$created_utc %||% NA_real_, comments$created_utc),
    stringsAsFactors = FALSE
  )
}

# if the cache exists and has content, use it; otherwise fetch fresh Reddit data.
reddit_cache <- "data/reddit_content.csv"
cache_ready <- file.exists(reddit_cache) && file.info(reddit_cache)$size > 1

if (cache_ready) {
  raw_df <- tryCatch(
    read.csv(reddit_cache, stringsAsFactors = FALSE),
    error = function(e) {
      message("Reddit cache could not be read: ", conditionMessage(e))
      data.frame()
    }
  )

  if (nrow(raw_df) > 0) {
    cat("Loaded Reddit content from cache:", nrow(raw_df), "\n")
  } else {
    message("Reddit cache is empty, fetching fresh data instead.")
    cache_ready <- FALSE
  }
}

if (!cache_ready) {
  reddit_posts <- tryCatch(
    find_thread_urls(keywords = "motorola razr 2025",
                     subreddit = "Android", sort_by = "top"),
    error = function(e) {
      message("Reddit search failed: ", conditionMessage(e))
      data.frame(url = character())
    }
  )

  cat("Reddit thread URLs found:", nrow(reddit_posts), "\n")

  raw_df <- if (nrow(reddit_posts) > 0) {
    tryCatch(
      fetch_reddit_thread(reddit_posts$url[1]),
      error = function(e) {
        message("Reddit content fetch failed: ", conditionMessage(e))
        data.frame()
      }
    )
  } else {
    message("No Reddit threads matched the search query.")
    data.frame()
  }

  # save the raw data to csv for future use and to avoid hitting api limits while developing
  write.csv(raw_df, reddit_cache, row.names = FALSE)
}

cat("Rows collected:", nrow(raw_df), "\n")
cat("Posts vs comments:\n")
print(table(raw_df$type))
```

```{r amazon-fetch, echo=TRUE}
# we fetched via outscrapper which was exported as a a csv so we just read the file here :)
# due to limitations with the api price, only a subset of reviews are collected, from a subset of razr products and georaphical locations (i.e us only)

#cat("Reviews collected:", nrow(amazon_reviews), "\n")
#cat("Rating distribution:\n")
#print(table(amazon_reviews$rating))
```

```{r youtube-fetch, echo=TRUE}
fetch_youtube_comments <- function(video_id, max_comments = 200, api_key = Sys.getenv("YOUTUBE_KEY")) {
  if (identical(api_key, "")) {
    stop("YOUTUBE_KEY is not set. Load it from .env or your environment before knitting.")
  }

  all_comments <- list()
  page_token   <- NULL

  repeat {
    query <- list(
      part       = "snippet",
      videoId    = video_id,
      maxResults = 100,
      textFormat = "plainText",
      key        = api_key
    )

    # Add pagination token if we have one
    if (!is.null(page_token)) {
      query$pageToken <- page_token
    }

    resp <- httr::GET(
      "https://www.googleapis.com/youtube/v3/commentThreads",
      query = query
    )

    if (httr::http_error(resp)) {
      error_body <- tryCatch(
        httr::content(resp, as = "text", encoding = "UTF-8"),
        error = function(e) ""
      )
      message("YouTube API error: ", httr::status_code(resp), if (nzchar(error_body)) paste0(" - ", error_body) else "")
      break
    }

    parsed <- jsonlite::fromJSON(
      httr::content(resp, as = "text", encoding = "UTF-8"),
      flatten = TRUE
    )

    # Extract top-level comments
    items <- parsed$items

    if (is.null(items) || nrow(items) == 0) break

    batch <- data.frame(
      comment_id    = items$id,
      author        = items$snippet.topLevelComment.snippet.authorDisplayName,
      body          = items$snippet.topLevelComment.snippet.textDisplay,
      like_count    = items$snippet.topLevelComment.snippet.likeCount,
      reply_count   = items$snippet.totalReplyCount,
      date          = items$snippet.topLevelComment.snippet.publishedAt,
      stringsAsFactors = FALSE
    )

    all_comments[[length(all_comments) + 1]] <- batch
    collected <- sum(sapply(all_comments, nrow))
    message("Collected: ", collected, " comments")

    # Check for next page
    page_token <- parsed$nextPageToken

    if (is.null(page_token) || collected >= max_comments) break

    Sys.sleep(0.5)
  }

  if (length(all_comments) == 0) return(data.frame())

  dplyr::bind_rows(all_comments) %>%
    dplyr::mutate(
      source  = "youtube",
      # Like count as proxy for sentiment strength
      segment = dplyr::case_when(
        like_count >= quantile(like_count, 0.66, na.rm = TRUE) ~ "positive",
        like_count <= quantile(like_count, 0.33, na.rm = TRUE) ~ "negative",
        TRUE ~ "neutral"
      )
    )
}
razr_videos <- list(
  mkbhd      = "8om1eJrO2lU",   # MKBHD Razr 2025 review
  dave2d     = "JTT67FSc8j8",   # shortCircuit review
  mrmobile   = "YGTkjchlVJk",   # MrMobile review
  phonearena = "b3Ijuf7DHcQ"    # PhoneArena review
)

# to save on api calls, we check if we have a local csv of comments already, if not we fetch and save for next time.
if (file.exists("data/youtube_comments.csv")) {
  youtube_all <- read.csv("data/youtube_comments.csv", stringsAsFactors = FALSE)
  cat("Loaded YouTube comments from CSV:", nrow(youtube_all), "\n")
} else {
  youtube_all <- purrr::map2_dfr(
    razr_videos,
    names(razr_videos),
  ~   fetch_youtube_comments(.x, max_comments = 200) %>%
        dplyr::mutate(channel = .y)
  )
  # Save to CSV for future runs
  write.csv(youtube_all, "data/youtube_comments.csv", row.names = FALSE);
}

cat("YouTube comments collected:", nrow(youtube_all), "\n")
print(table(youtube_all$channel))
```

# Pre-Processing
Side note maybe we dont have to do all of them based on the quality of the data we get, but we should at least explain how we would do them and why they are important.
## Filtering & Cleaning
Explain how we cleaned the data and why.

## Tokenization
Explain how we tokenized the data and why.

## Stop Words Removal
Explain how we removed stop words and why.

## Stemming & Lemmatization

## Frequency Filter

## Synonym consolidation

## Summary Statistics

# Topic Modeling (LDA)

## Build Document

## Optimal K

## Fit Model

## Stability

# Results

## Topic Word Distributions

## Sometother shit

# Reflection