---
title: "High Tech Marketing Text Analysis"
subtitle: "Brand: Motorola Razr 2025"
author: "Group 12?"
output:
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
#setup packages and stuff, include false so it doesn't show up.
# Set the CRAN mirror:
local({r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/"
  options(repos = r)}
)
# Install the packages used in this workbook:
packages <- c("RedditExtractoR", "httr", "jsonlite", "tidytext", "dplyr", "ggplot2", "wordcloud", "topicmodels", "LDAvis", "stringr", "purrr", "quanteda", "sentimentr", "cld2", "seededlda", "textstem")
for (i in packages) {
  if (!require(i, character.only = TRUE)) {
    install.packages(i, dependencies = TRUE)
    if (!require(i, character.only = TRUE)) {
      stop(paste("Package", i, "could not be loaded even after installation."))
    }
  }
}

#load the libraries
library(RedditExtractoR)
library(httr)
library(jsonlite)
library(tidytext)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(topicmodels)
library(LDAvis)
library(stringr)
library(purrr)
library(quanteda)
library(sentimentr)
library(seededlda)
library(cld2)
library(textstem)

env_file <- ".env"
if (requireNamespace("knitr", quietly = TRUE)) {
  input_file <- knitr::current_input()
  if (!is.null(input_file)) {
    env_file <- file.path(dirname(input_file), ".env")
  }
}

if (file.exists(env_file)) {
  readRenviron(env_file)
} else if (file.exists(".env")) {
  readRenviron(".env")
}

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x
```

# Introduction
Explain shit here philippe 8=====D

# Sample Selection
We decided to go with mulitiple sources of text in an attempt to capture multiple perspectives on the Razr and avoid pigeon hollling into one corner of the internet which may have skewed results. 

## Data Sources
We grabbed our shit from Reddit threads about the Motorola Razr 2025 (pain in my ass) and Youtube comments from popular tech youtubers who reviewed the Razr 2025

## Sampling representation & Bias
Explain if the sample is representative of all customers, and how platform choice may skew results e.g Reddit chuds are not normal people.

# Data Collection
```{r reddit-fetch, echo=TRUE}
fetch_reddit_thread <- function(thread_url, limit = 500, attempts = 5) {
  api_url <- paste0(thread_url, ".json?limit=", limit)
  response <- RETRY(
    "GET",
    api_url,
    user_agent(paste0("Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) ",
                      "AppleWebKit/537.36 (KHTML, like Gecko) ",
                      "Chrome/125.0.0.0 Safari/537.36")),
    times        = attempts,
    pause_base   = 2,
    pause_cap    = 20,
    terminate_on = c(400, 401, 403, 404)
  )

  if (http_error(response)) {
    stop("HTTP ", status_code(response), " when fetching ", api_url)
  }

  payload <- fromJSON(
    content(response, as = "text", encoding = "UTF-8"),
    simplifyVector = FALSE
  )
  post <- payload[[1]]$data$children[[1]]$data

  flatten_comments <- function(children) {
    if (!is.list(children)) return(data.frame())
    rows <- list()
    for (child in children) {
      if (!is.null(child$kind) && child$kind == "t1") {
        comment   <- child$data
        body_text <- comment$body %||% NA_character_
        if (!is.null(body_text)) body_text <- gsub("[\r\n]+", " ", body_text)
        rows[[length(rows) + 1]] <- data.frame(
          type      = "comment",
          id        = comment$id        %||% NA_character_,
          parent_id = comment$parent_id %||% NA_character_,
          author    = comment$author    %||% NA_character_,
          body      = body_text,
          score     = comment$score     %||% NA_real_,      # keep score for segmentation
          subreddit = comment$subreddit %||% NA_character_, # keep subreddit for segmentation
          stringsAsFactors = FALSE
        )
        replies <- if (is.list(comment$replies) &&
                       !is.null(comment$replies$data$children))
          comment$replies$data$children else list()
        if (length(replies) > 0)
          rows <- c(rows, flatten_comments(replies))
      }
    }
    if (length(rows) == 0) return(data.frame())
    rows <- Filter(function(x) is.data.frame(x) && ncol(x) > 0, rows)
    if (length(rows) == 0) return(data.frame())
    tryCatch(
      dplyr::bind_rows(rows),
      error = function(e) {
        cols     <- c("type","id","parent_id","author","body","score","subreddit")
        repaired <- lapply(rows, function(r) {
          if (!is.data.frame(r)) return(NULL)
          for (m in setdiff(cols, names(r))) r[[m]] <- NA
          r[cols]
        })
        dplyr::bind_rows(Filter(Negate(is.null), repaired))
      }
    )
  }

  comments  <- flatten_comments(payload[[2]]$data$children %||% list())
  post_body <- post$selftext %||% post$title %||% NA_character_
  if (!is.null(post_body)) post_body <- gsub("[\r\n]+", " ", post_body)

  post_df <- data.frame(
    type      = "post",
    id        = post$id     %||% NA_character_,
    parent_id = NA_character_,
    author    = post$author %||% NA_character_,
    body      = post_body,
    score     = post$score  %||% NA_real_,
    subreddit = post$subreddit %||% NA_character_,
    stringsAsFactors = FALSE
  )

  if (!is.data.frame(comments)) comments <- data.frame()
  tryCatch(
    dplyr::bind_rows(post_df, comments),
    error = function(e) post_df
  )
}

suppressWarnings({
  reddit_cache <- "data/reddit_content.csv" 
  cached <- file.exists(reddit_cache)

  if (cached) {
    reddit_all <- tryCatch(
      read.csv(reddit_cache, stringsAsFactors = FALSE),
      error = function(e) { message("Cache read failed: ", conditionMessage(e)); data.frame() }
    )
  }
  else {
    search_config <- list(
      list(sub = "Android",       kw = "motorola razr"),
      list(sub = "Android",       kw = "razr 2025"),
      list(sub = "Android",       kw = "razr flip"),
      list(sub = "Motorola",      kw = "razr"),
      list(sub = "Motorola",      kw = "razr ultra"),
      list(sub = "Motorola",      kw = "razr plus"),
      list(sub = "phones",        kw = "razr"),
      list(sub = "phones",        kw = "motorola"),
      list(sub = "smartphones",   kw = "motorola razr"),
      list(sub = "razr",          kw = "razr"),
      list(sub = "razr",          kw = "motorola"),
      list(sub = "technology",    kw = "motorola razr"),
      list(sub = "technology",    kw = "razr 2025")
    )

    reddit_posts <- dplyr::bind_rows(Filter(
      function(x) is.data.frame(x) && nrow(x) > 0,   # add this Filter wrapper
      lapply(search_config, function(cfg) {
        result <- tryCatch({
          Sys.sleep(2)
          find_thread_urls(keywords = cfg$kw, subreddit = cfg$sub, sort_by = "top")
        }, error = function(e) {
          message("Failed r/", cfg$sub, " / '", cfg$kw, "': ", conditionMessage(e))
          data.frame(url = character())  # always return a data frame, never NULL
        })
        cat("r/", cfg$sub, "/ '", cfg$kw, "' ->", 
            if (is.data.frame(result)) nrow(result) else "ERROR", "threads\n")
        # Ensure we always return a data frame regardless of what find_thread_urls gives back
        if (!is.data.frame(result)) return(data.frame(url = character()))
        result
      })
    )) |> dplyr::distinct(url, .keep_all = TRUE)

    cat("Total unique threads:", nrow(reddit_posts), "\n")

    reddit_max_threads <- 250

    if (nrow(reddit_posts) > 0) {
      to_fetch <- head(reddit_posts$url, reddit_max_threads)
      raw_list <- lapply(seq_along(to_fetch), function(i) {
        Sys.sleep(1)
        message("Thread ", i, "/", length(to_fetch))
        tryCatch(
          fetch_reddit_thread(to_fetch[i]),
          error = function(e) {
            message("Failed: ", conditionMessage(e))
            data.frame()
          }
        )
      })
      reddit_all <- dplyr::bind_rows(
        Filter(function(x) is.data.frame(x) && nrow(x) > 0, raw_list)
      )
    } else {
      reddit_all <- data.frame()
    }

    write.csv(reddit_all, reddit_cache, row.names = FALSE) 
  }
})

cat("Total rows:", nrow(reddit_all), "\n")
cat("Posts vs comments:\n")
print(table(reddit_all$type))
cat("By subreddit:\n")
print(table(reddit_all$subreddit))
```

```{r youtube-fetch, echo=TRUE}
fetch_youtube_comments <- function(video_id, max_comments = 400, api_key = Sys.getenv("YOUTUBE_KEY")) {
  if (identical(api_key, "")) {
    stop("YOUTUBE_KEY is not set. Load it from .env or your environment before knitting.")
  }

  all_comments <- list()
  page_token   <- NULL

  repeat {
    query <- list(
      part       = "snippet",
      videoId    = video_id,
      maxResults = 200,
      textFormat = "plainText",
      key        = api_key
    )

    # Add pagination token if we have one
    if (!is.null(page_token)) {
      query$pageToken <- page_token
    }

    resp <- httr::GET(
      "https://www.googleapis.com/youtube/v3/commentThreads",
      query = query
    )

    if (httr::http_error(resp)) {
      error_body <- tryCatch(
        httr::content(resp, as = "text", encoding = "UTF-8"),
        error = function(e) ""
      )
      message("YouTube API error: ", httr::status_code(resp), if (nzchar(error_body)) paste0(" - ", error_body) else "")
      break
    }

    parsed <- jsonlite::fromJSON(
      httr::content(resp, as = "text", encoding = "UTF-8"),
      flatten = TRUE
    )

    # Extract top-level comments
    items <- parsed$items

    if (is.null(items) || nrow(items) == 0) break

    batch <- data.frame(
      comment_id    = items$id,
      author        = items$snippet.topLevelComment.snippet.authorDisplayName,
      body          = items$snippet.topLevelComment.snippet.textDisplay,
      stringsAsFactors = FALSE
    )

    all_comments[[length(all_comments) + 1]] <- batch
    collected <- sum(sapply(all_comments, nrow))
    message("Collected: ", collected, " comments")

    # Check for next page
    page_token <- parsed$nextPageToken

    if (is.null(page_token) || collected >= max_comments) break

    Sys.sleep(0.5)
  }

  if (length(all_comments) == 0) return(data.frame())
  dplyr::bind_rows(all_comments) |> dplyr::mutate(source = "youtube");
}
razr_videos <- list(
  mkbhd      = "8om1eJrO2lU",   # MKBHD Razr 2025 review
  dave2d     = "JTT67FSc8j8",   # ShortCircuit review
  mrmobile   = "YGTkjchlVJk",   # MrMobile review
  phonearena = "b3Ijuf7DHcQ"    # PhoneArena review
)

# to save on api calls, we check if we have a local csv of comments already, if not we fetch and save for next time.
if (file.exists("data/youtube_comments.csv")) {
  youtube_all <- read.csv("data/youtube_comments.csv", stringsAsFactors = FALSE)
  cat("Loaded YouTube comments from CSV:", nrow(youtube_all), "\n")
} else {
  youtube_all <- purrr::map2_dfr(
    razr_videos,
    names(razr_videos),
  ~   fetch_youtube_comments(.x, max_comments = 400) %>%
        dplyr::mutate(channel = .y)
  )
  # Save to CSV for future runs
  write.csv(youtube_all, "data/youtube_comments.csv", row.names = FALSE);
}

cat("YouTube comments collected:", nrow(youtube_all), "\n")
print(table(youtube_all$channel))
```
# Exploration
Lets have a gander at the data we collected and see if theres any thing fun before we clean it up. 
```{r exploration, echo=TRUE}
# reddit 
str(reddit_all)
# youtube
str(youtube_all)
```
# Pre-Processing
we have 2 separate data frames for reddit, and youtube, we need to merge them into one big one for the text analysis. We can add a column to indicate the source of each row and then bind them together.
```{r merge-data, echo=FALSE}
# merge data frames by piping them so i dont lose my mind. keep like count for youtube, keep score for reddit.
reddit_clean <- reddit_all |> filter(type == "comment", !is.na(body), body != "[deleted]", body != "[removed]", nchar(trimws(body)) > 20) |> select(author, body, score, subreddit) |> rename(source = subreddit)

youtube_clean <- youtube_all |>
  mutate(
    score = if ("like_count" %in% names(youtube_all)) youtube_all$like_count else NA_real_,
    source = channel
  ) |>
  select(author, body, score, source)

combined_data <- dplyr::bind_rows(reddit_clean, youtube_clean)

# create unique id for each row
combined_data <- combined_data |> mutate(id = row_number())

# assign language
combined_data$language <- cld2::detect_language(combined_data$body)
head(cbind(table(combined_data$language)), 20) 

```
Side note maybe we dont have to do all of them based on the quality of the data we get, but we should at least explain how we would do them and why they are important.

## Filtering & Cleaning
```{r data-cleaning, echo=TRUE}
#remove non english comments
combined_data <- combined_data |> filter(language == "en")

#remove shit
combined_data$body <- gsub("[^\x01-\x7F]", "", combined_data$body)

#remove empty bodies
combined_data <- combined_data |> filter(body != "")
```

# Modeling

## Corpus Creation
```{r corpus-creation, echo=TRUE}
corpus <- quanteda::corpus(combined_data, docid_field = "id", text_field = "body")

summary(corpus, 10)

as.character(corpus[ sample(length(corpus), 1) ])

quanteda::docvars(corpus, field = "ave_sentiment") <- sentimentr::sentiment_by(sentimentr::get_sentences(corpus))$ave_sentiment

hist(quanteda::docvars(corpus)$ave_sentiment)

as.character(corpus[ which(quanteda::docvars(corpus)$ave_sentiment == summary(quanteda::docvars(corpus)$ave_sentiment)[1]), ])
as.character(corpus[ which(quanteda::docvars(corpus)$ave_sentiment == summary(quanteda::docvars(corpus)$ave_sentiment)[6]), ])
```
## Tokenization
Explain how we tokenized the data and why.
```{r tokenization}
tokens <- quanteda::tokens(corpus, 
                           what = "word", # text unit to extract
                           remove_punct = TRUE,
                           remove_symbols = TRUE,
                           remove_numbers = TRUE,
                           remove_url = TRUE,
                           remove_separators = TRUE,
                           split_hyphens = FALSE,
                           split_tags = FALSE,
                           include_docvars = TRUE,
                           padding = FALSE,
                           verbose = TRUE)
tokens[ sample(length(tokens), 1) ]

tokens <- quanteda::tokens_tolower(tokens)
```

## Stop Words Removal
```{r stop-words, echo=TRUE}
quanteda::stopwords("en")
custom_stops <- c(
  "razr", "motorola", "phone", "just", "get", "like", "thing", "really", "know", "time", "people", "would", "also", "much", "use", "see",
  "one", "will", "can", "also", "even", "still", "want", "review",
  "moto", "device", "smartphone", "im", "dont", "ive", "thats", "got", "amp",
  "u", "ur", "ok", "yeah", "lol", "gonna", "screen", "use", "good", "get", "make", "think", "need", "look", "come", "say"
)
tokens <- quanteda::tokens_remove(tokens, pattern = c(quanteda::stopwords("en"), custom_stops))
```

## Stemming & Lemmatization
```{r stemming, echo=TRUE}
tokens <- quanteda::tokens_replace(tokens, pattern = quanteda::featnames(quanteda::dfm(tokens)),replacement = textstem::lemmatize_words(quanteda::featnames(quanteda::dfm(tokens)))
)
```

## DFM Creation & Frequency Filtering
```{r frequency-filter, echo=TRUE}
dfm <- quanteda::dfm(tokens)

dfm <- quanteda::dfm_select(dfm, pattern     = "^.{3,}$", valuetype   = "regex", selection   = "keep")

dfm

dfm <- dfm_trim(dfm, min_termfreq = 10)
dfm

topfeatures(dfm)

length_features <- data.frame(count = quanteda::topfeatures(dfm, ncol(dfm))) # create data frame 
length_features$length <- nchar(rownames(length_features)) # extract token length
length_features[ which(length_features$length %in% c(1, 2)), ] # filter on token length

dfm <- dfm[ -which((rowSums(dfm)) %in% 0), ]
```

## Synonym consolidation
```{r synonym-consolidation, echo=TRUE}
# Add this chunk under ## Synonym consolidation
# Simple flat vectors — pattern and replacement must be same length
tokens <- quanteda::tokens_replace(tokens,
  pattern = c(
    # Form factor
    "fold", "foldable", "folding",
    "flip", "flipping",
    # Camera
    "cam", "cams",
    # Battery
    "charging", "charger",
    # Display (already have "screen" as stop word — keep display as synonym)
    "display", "displays",
    # Hinge
    "hinges", "hinging",
    # Price
    "pricing", "priced", "pricey", "expensive", "costly",
    # Competitors
    "galaxy",
    "iphone", "ios", "apple"
  ),
  replacement = c(
    # Form factor
    "fold", "fold", "fold",
    "flip", "flip",
    # Camera
    "camera", "camera",
    # Battery
    "charge", "charge",
    # Display
    "screen", "screen",
    # Hinge
    "hinge", "hinge",
    # Price
    "price", "price", "price", "price", "price",
    # Competitors
    "samsung",
    "apple", "apple", "apple"
  ),
  valuetype = "fixed"
)
```
##  LDA
```{r topic-modeling, echo=TRUE}

dtm <- quanteda::convert(dfm, to = "topicmodels")

# Split DTM into train/test for perplexity evaluation
set.seed(42)
n_docs      <- nrow(dtm)
train_idx   <- sample(n_docs, floor(n_docs * 0.8))
dtm_train   <- dtm[train_idx, ]
dtm_test    <- dtm[-train_idx, ]

# Test k values from 2 to 15
k_values <- 2:15

perplexity_scores <- sapply(k_values, function(k) {
  cat("Fitting k =", k, "\n")
  m <- topicmodels::LDA(
    dtm_train,
    k       = k,
    method  = "Gibbs",
    control = list(seed = 42, iter = 1000, burnin = 200)
  )
  topicmodels::perplexity(m, newdata = dtm_test)  # evaluate on held-out test set
})

# Plot
perplexity_df <- data.frame(k = k_values, perplexity = perplexity_scores)

ggplot(perplexity_df, aes(x = k, y = perplexity)) +
  geom_line(colour = "#2C7BB6") +
  geom_point(colour = "#2C7BB6", size = 2) +
  labs(title = "Held-out Perplexity by Number of Topics (k)",
       subtitle = "Lower = better generalisation; choose the elbow",
       x = "k", y = "Perplexity") +
  theme_minimal()

print(perplexity_df)

K <- 7 # choose based on the plot.

lda_model <- seededlda::textmodel_lda(dfm, k = K)

# Then analyse sentiment per topic after the fact
topic_assignments <- data.frame(
  doc_id    = docnames(dfm),
  topic     = topics(lda_model),
  sentiment = docvars(dfm)$ave_sentiment
)

# Average sentiment per topic — this is your comparison
topic_sentiment <- topic_assignments |>
  group_by(topic) |>
  summarise(mean_sentiment = mean(sentiment, na.rm = TRUE),
            n = n())

# Visualize sentiment distribution across topics.
ggplot(topic_sentiment, aes(x = factor(topic), y = mean_sentiment)) +
  geom_bar(stat = "identity", fill = "#2C7BB6") +
  labs(title = "Average Sentiment by Topic",
        x = "Topic", y = "Average Sentiment") +
  theme_minimal()
  
# You can also look at the distribution of sentiment within each topic:
ggplot(topic_assignments, aes(x = factor(topic), y = sentiment)) +
  geom_boxplot(fill = "#2C7BB6") +
  labs(title = "Sentiment Distribution by Topic",
        x = "Topic", y = "Sentiment") +
  theme_minimal()
```

## Improving the model
```{r improving-model, echo=TRUE}

```

## Stability Analysis
```{r stability-analysis, echo=TRUE}
seeds <- c(42L, 123L, 999L)

stability_results <- lapply(seeds, function(s) {
  set.seed(s)
  m     <- seededlda::textmodel_lda(dfm, k = K)
  terms <- seededlda::terms(m, 5)  # matrix: 5 rows (words) x K cols (topics)
  # Collapse each topic's top 5 words into one string per topic
  apply(terms, 2, paste, collapse = ", ")  # returns named vector of length K
})

# Each result is a named vector of length K — bind into a clean table
stability_df <- data.frame(
  topic    = paste0("Topic ", 1:K),
  seed_42  = stability_results[[1]],
  seed_123 = stability_results[[2]],
  seed_999 = stability_results[[3]],
  row.names = NULL
)

knitr::kable(stability_df,
             col.names = c("Topic", "Seed 42", "Seed 123", "Seed 999"),
             caption   = "Top 5 words per topic across 3 seeds (stability check)")

```
# Results
```{r results, echo=TRUE}
# Show top 10 words per topic with your human-readable label
topic_terms <- seededlda::terms(lda_model, 10)
knitr::kable(topic_terms, caption = "Top 10 terms per topic")

# TODO: label each topic based on dominant terms, e.g.:
# topic1 = "Price & Value", topic2 = "Camera Quality", etc.

topic_counts <- as.data.frame(table(topics(lda_model))) |>
  rename(topic = Var1, n = Freq) |>
  mutate(prop = n / sum(n))

ggplot(topic_counts, aes(x = reorder(topic, prop), y = prop)) +
  geom_col(fill = "#2C7BB6") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Topic Prominence",
       x = NULL, y = "Proportion of documents") +
  theme_minimal()

  # Merge topic assignments back with source info
topic_source <- topic_assignments |>
  mutate(doc_id = as.integer(doc_id)) |>
  left_join(combined_data |> select(id, source), 
            by = c("doc_id" = "id"))

contingency <- table(topic_source$topic, topic_source$source)
knitr::kable(contingency, caption = "Topic distribution by source")

chi_result <- chisq.test(contingency)
print(chi_result)
# Interpret: p < 0.05 means Reddit and YouTube discuss different topics
```

## Topic Word Distributions

## Sometother shit

# Reflection